---
title: "Develop models to predict sentiment"
author: "Mauricio_Carvajal"
date: "22/3/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```
# 1. Libraries
Loading the libraryes
```{r message=FALSE}
library(doParallel)
library(plotly)
library(caret) #caret-->clasificacion and regresion testing
library(C50)
library(plotrix)
library(ggplot2)
library(corrplot)
library(varImp)
library(e1071)  # For SVN
library(kknn)   # For KNN
library(dplyr)
```

# 2. Set up Parallel Processing


2.1 Find how many cores are on your machine
detectCores() # Result = Typically 4 to 6, I have 8 core so I will use 6
2.2 Create Cluster with desired number of cores. Don't use them all! Your computer is running other processes.
```{r}
cl <- makeCluster(4)
```
2.3. Register Cluster
```{r}
registerDoParallel(cl)
```
2.4 Confirm how many cores are now "assigned" to R and RStudio
```{r}
getDoParWorkers() # Result 6, due to I have 8 core
```
Stop Cluster. After performing your tasks, stop your cluster.
```{r }
stopCluster(cl)
```{r}


